---
title: "Helpers' Document"
format: html
---

In this file, all the code bits that need pasting into the collaborative doc will be, as well as some helpful tips to the helpers for this workshop. After a workshop has run, I'd greatly appreciate any help in improving the helper doc for future workshops, so if you have ideas let me know. If you are comfortable with GitHub, a PR directly to this repo with suggestions is highly appreciated.

## Open tabs

During the workshop, I think its a good idea for helpers to have on their computers certain tabs open at all times, so you can easily navigate to them at need

-   the collaborative document  
-   the workshop website  
-   the slides the instructor is currently running through  

## Schedule

{{< include child_docs/schedule.qmd >}}


## Frequently seen issues

### Markdown formatting is not being applied

-   Make sure the file is saved as .qmd, not .md  
-   When in the visual editor, if typing in markdown syntax, the editor add an [escape character](https://www.wikiwand.com/en/Escape_character) to the markdown, which will not be rendered. - To see this, have them switch to the `source` editor in stead, and look for stray backslashes (`\`) in the markdown, this is the escape character. Have them delete that and try again. Once fixed, that can switch back to the visual editor.   - If the learner knows a lot of plain markdown, they can also just use the source editor, but I find that the visual editor is a good way to get started. I usually switch between the two a lot.  

## Workshop progression

In this section, we have anything that is related to the workshop as it is progressing. Each section has its own subtitle here, and these should also match sections in the collaborative document. This way, helpers can easily navigate to the relevant section in the helper document.

### Intro

Slides: <https://drmowinckels.io/quartaki/00_intro.html#/title-slide>

The intro section does not contain any exercises or code to copy. This part is mainly information and links to further resources for the learners.

#### What you should be doing

-   Look out for questions in the collaborative doc  
-   Help me notice raised hands I might not see  
-   Help paste urls and resources asked for in the collaborative doc  

### Markdown elements

Slides: <https://drmowinckels.io/quartaki/01_elements.html#/title-slide>

This section also has no exercise, it is another very quick information run down. This is intended as a very brief glimpse into plain markdown formatting, and we will not spend time on this as lecture, but will be doing it in practice together later. It is meant as a quick reference for the learners in the workshop, for later exercises.

#### What you should be doing

-   Look out for questions in the collaborative doc  
-   Help me notice raised hands I might not see  
-   Help paste urls and resources asked for in the collaborative doc  

### Presentation - live demos

Slides: <https://drmowinckels.io/quartaki/02_presentation.html#/title-slide>

This section is where we start live coding and working together on a document. The documents we are working towards can be found in their entirety in [/example_files](/example_files) of this repository.

We start with html, then pdf, and lastly html presentations at the end.

#### HTML

##### 1

###### Live demo section

{{< include child_docs/demos/01_new-doc.qmd >}}


###### Exercise section

{{< include child_docs/exercises/01_make-list.qmd >}}


**Notes**   

1. They should just write some simple sentences in the document. There is a <Lorem Ipsum> at the bottom of the collaborative doc, if people want to test a large bulk of text.

1. Making a list means using the markdown syntax for lists. Learners can use [markdown guide](https://quarto.org/docs/authoring/markdown-basics.html#lists) or look at the slides from the markdown elements session to see how to do that.

1. This means changing the markdown syntax for lists to an ordered list. Learners can use [markdown guide](https://quarto.org/docs/authoring/markdown-basics.html#lists) or look at the slides from the markdown elements session to see how to do that.

##### 2

###### Live demo section

{{< include child_docs/demos/02_yaml-test.qmd >}}


###### Exercise section

Here, learners should learn to explore what can be done in the yaml section, so that they get an idea of what is possible and how to explore the possibilities.

::: tip
One helpful thing here is that RStudio can provide suggestions once they type in three characters in the yaml, and then they can flip through the possible suggestions. It will also provide suggestions for values that are possible for that option. Learners can use [html guide](https://quarto.org/docs/output-formats/html-basics.html) for possible alternatives
:::

{{< include child_docs/exercises/02_alter-yaml.qmd >}}
 
**Notes**   

1. This means changing the yaml option for the title of the `toc-title`.  
1. This is done through the `toc-location` option  
1. This is done through the `anchor-sections: true` option  
1. This is done through the `smooth-scroll: true` option  

##### 3

###### Live demo section

```{r}
#| child: child_docs/demos/03_visual-ed.qmd
```

Code chunks we will be adding during this demo section

```{r}
#| child: child_docs/examples/01_setup.qmd
```

```{r}
#| child: child_docs/examples/02_penguins-scatter.qmd
```

```{r}
#| child: child_docs/examples/03_penguins-density.qmd
```

###### Exercise section

{{< include child_docs/exercises/03_add-elements.qmd >}}

**Notes**   
1. This means adding a block with the `::: tip` option  
1. This means adding a block with the `---` option  
1. code comments are normal `#` comments  
    - text comments are `<!-- text -->`  

##### 4

###### Live demo section

Showing how we add cross references to figures and tables

{{< include child_docs/demos/04_cross-refs.qmd >}}

We add the necessary pieces of information to the plot code chunk

{{< include child_docs/examples/04_penguins-scatter_opts.qmd >}}

and reference with `@fig-penguin-smooth`

{{< include child_docs/examples/05_penguins-density_opts.qmd >}}

and reference with `@fig-penguin-density`

{{< include child_docs/examples/06_penguins-table.qmd >}}


and reference with `@tbl-penguins`

###### Exercise section

{{< include child_docs/exercises/04_add-image.qmd >}}

**Notes**   

1. They can copy+paste an image straight into the visual editor  
    -   They can also use the `Insert` button in the visual editor to add an image  
    -   They can also use the markdown syntax for images to add an image  
    -   To give this a label they need to give it a "label" (or an ID) either in the markdown code, or through the attributes in the visual editor  

1. This means adding a caption to the image, and then referencing it with `@fig-label`  
    -   caption can be added either as markdown, or through double clicking the image and adding it in the visual editor  

##### 5

###### Live demo section

{{< include child_docs/demos/05_citation-tool.qmd >}}


inform about zotero and better bibtex integration

###### Exercise section


{{< include child_docs/exercises/05_add-citation.qmd >}}

**Notes**   

1. They need to open the citation too, search for a paper, and "add citation"  
1. **standard** default, no changes just `@ref-text`  
    -  **extra page information** `[@ref-text, p.XX and other text needed]`  
    -  **year only** `[-@ref-text]`  

#### PDF

##### 6

###### Live demo section

```{r}
#| child: child_docs/demos/06_to-pdf.qmd
```

###### Exercise section

{{< include child_docs/exercises/06_pdf-yaml.qmd >}}

**Notes**    

1. Adding headers either in the markdown (`##`) or in the visual editor  
1. Adding section numbering in the yaml `number-sections: true`  

#### Presentations

##### 7

###### Live demo section

{{< include child_docs/demos/07_to-reveal.qmd >}}

###### Exercise section

{{< include child_docs/exercises/07_to-reveal.qmd >}}

**Notes**   

1. this is done by making more headers  
1. adding three `---` where a new slide should start  
1. best done with visual editor looking for `/columns` in the insert menu  
