---
title: "Quartaki"
subtitle: "--- 6 hour introduction to Quarto ---"
author: Athanasia Mo Mowinckel
---

There are increasing demands on scientific staff in preparing reports for governmental and public dissemination, as well as scientific dissemination. Creating reports is a time-consuming task, as it often requires switching between programs for writing, doing analyses and creating tables and figures, as well as other graphical and textual programs. Learning efficient tools in combining programming and report generation are becoming increasingly important to alleviate the manual and burdensome process of switching programs. \
\
Quarto is a second generation report framework based on the popular markdown plain text format. Combining writing in markdown
with the ability to run code to format, analyse, and visualise data, all in the
same place, creates a seamless environment for the researchers to produce
reports. \
\
While this workshop will focus on using Quarto with R, it also has
native abilities to interact with python, observable.js and Julia, without
needing R installed. This makes Quarto a great tool to learn, no matter which
language you focus on.

::: callout-tip
## Aims

-   Understand the basics of markdown

-   Ability to generate html & pdf reports, and presentations

-   Ability to cross-reference report content and add citations

-   Be able to use Academic Journal templates
:::

```{r}
#| child: schedule.qmd
```

# Preparations

This introductory workshop to Quarto is being instructed using R and RStudio. It would be easiest for learners to follow along, and the istructor to help you , if you also use this set-up.

Install instructions can be found on the [RStudio webpages](https://quarto.org/docs/get-started/).

A new version of [RStudio](https://www.rstudio.com/products/rstudio/download/#download) and [R](https://cran.r-project.org/) is also recommended.

You may choose to use vscode or another IDE, or even to do python in stead of R. However, know that the instructor will be less available to help using these tools, and code examples will need to be thought of by the learners them selves. Some examples on using other setups than R and RStudio can be found on the [Quarto webpages](https://quarto.org/docs/get-started/hello/vscode.html).

## R packages

In addition to Quarto, a series of R packages will also be needed to show-case the ways we can use Quarto to generate reports.

```{r}
#| eval: false
# Run in R
install.packages(c(
  "tidyverse",     # data-wrangling
  "broom",         # model tidying
  "knitr",         # table printing
  "kableExtra",    # pretty table printing
  "palmerpenguins" # dataset
))
```



If you have problems getting things installed, please [contact me](mailto:a.m.mowinckel@psykologi.uio.no), and I will try help you get sorted.
