---
format: markdown_github
---

# Quintro

--- 6 hour introduction to Quarto ---

<!-- badges: start -->

[![](https://github.com/drmowinckels/quartaki/actions/workflows/publish.yaml/badge.svg)](https://github.com/drmowinckels/quartaki/actions/workflows/publish.yaml) ![Contributors](https://img.shields.io/github/contributors/drmowinckels/quartaki) ![GitHub last commit](https://img.shields.io/github/last-commit/drmowinckels/quartaki)

<!-- badges: end -->

```{r}
#| child: child_docs/intro.qmd
```

```{r}
#| child: child_docs/aims.qmd
```

## Schedule

```{r}
#| child: child_docs/schedule.qmd
```

## Prepare

```{r}
#| child: child_docs/prep.qmd
```

## Instructor's notes

The sections of the workshop are intended to be run in sequence, as they prepare the learners for the section coming.
Changing the order of the sections would also mean adapting content to make sure you don't skip ahead from where the learners are.
In particular, the sections after lunch have little presentation, but mostly live coding and working.

The [course website](https://drmowinckels.github.io/quartaki/) should contain most of the materials for learners to follow along presentations and the schedule.

The output examples are found in their [own folder](example_files/), and have the entire code for the final outputs, after all parts of their respective section has been covered.

In most cases, after the text and code chunks have been written, the course focuses on adapting yaml settings for the different format types.

## Code of Conduct

Please note that the quartaki project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
