---
title: "Palmer penguins"
author: Athanasia Mo Mowinckel
date: 2022-10-26
format: 
  html:
    toc: true
    toc-depth: 2
    toc-title: Contents
    toc-location: left
    html-math-method: katex
    css: lcbc-styles.scss
    anchor-sections: true
    smooth-scroll: true
    code-fold: true
    code-summary: "Show the code"
    embed-resources: true
    self-contained-math: true
editor: visual
execute: 
  warning: false
  message: false
  echo: true
---

```{r}
#| include: false

library(palmerpenguins)
library(knitr)
library(kableExtra)
library(tidyverse)
penguins <- penguins

```

\
We can write text as normal, interspersed with code that outputs something. We can choose to have the code shown or hidden, or provide the reader with the option to see the code if they wish.

My favourite foods:

1.  Souvlaki
2.  Pasta with halloumi
3.  Makaronia tou fournou (greek style lasagna)

We can also reference the figures @fig-penguin-smooth and @fig-penguin-density

```{r}
#| label: fig-penguin-smooth
#| fig-cap: Penguin bill length and depth ratio by species

ggplot(penguins,
       aes(x = bill_length_mm,
           y = bill_depth_mm)) +
  geom_point(aes(colour = species)) +
  geom_smooth(method = "lm", 
              color = "black") +
  theme_minimal()
```

And the order of the figures does not really matter. If you change the order to the figures, but keep their labels, no references will be broken in the report. We can also incorporate text derived from data to look as if it were "normal" text. Like the number of rows in the data being `r nrow(penguins)`, and the number of female penguins being `r filter(penguins, sex == "female") |> nrow()`. We can also add footnotes[^1], and they will keep themselves numbered and placed correctly[^2]

[^1]: which can be very convenient

[^2]: without us really needing to keep it all in mind.

```{r}
#| label: fig-penguin-density
#| fig-cap: Penguin density

penguins |> 
  ggplot(aes(x = bill_length_mm,
             fill = species)) + 
  geom_density() +
  theme_minimal()
```

A summary of the observed penguin data can be found in @tbl-penguins. For this cross-reference to work, we *need* to have the `tbl-` prefix in the label name of the chunk that creates the table. The number of the table will update if another table appears before it, meaning you no longer need to deal with number your content correctly.\

```{r}
#| label: tbl-penguins
#| tbl-cap: Penguin summary

penguins |> 
  pivot_longer(contains("_"),
               values_drop_na = TRUE) |> 
  group_by(name, species) |> 
  summarise(across(value, 
                   list(Mean = mean, 
                        SD = sd,
                        Min = min,
                        Max = max,
                        N = length),
                   .names = "{.fn}")) |> 
  mutate(
    name = str_replace_all(name, "_", " ")
  ) |> 
  kable(booktabs = TRUE, digits = 3,) |> 
  kable_classic() |> 
  add_header_above(c(" " = 4, "Range" = 2, " " = 1)) |> 
  collapse_rows(1)
```
