---
title: "Palmer penguins"
author: Athanasia Mo Mowinckel
date: 2022-10-26
format:
  revealjs: 
    slide-number: c/t
    incremental: true
    chalkboard: true
editor: visual
execute: 
  echo: true
  warning: false
  message: false
---

```{r}
#| include: false

library(palmerpenguins)
library(knitr)
library(kableExtra)
library(tidyverse)
penguins <- penguins

```

## Text

We can write text as normal, interspersed with code that outputs something. We can choose to have the code shown or hidden, or provide the reader with the option to see the code if they wish. We can also reference the figures @fig-penguin-smooth and @fig-penguin-density

::: .fragment
## Code

```{r}
#| label: fig-penguin-smooth
#| fig-cap: Penguin bill length and depth ratio by species
#| output-location: fragment

ggplot(penguins,
       aes(x = bill_length_mm,
           y = bill_depth_mm)) +
  geom_point(aes(colour = species)) +
  geom_smooth(method = "lm", 
              color = "black")
```
:::


# Another slide

::: columns
::: {.column width="50%"}
And the order of the figures does not really matter.
:::

::: {.column width="50%"}
If you change the order to the figures, but keep their labels, no references will be broken in the report.
:::
:::

## Inline computation

Like the number of rows in the data being `r nrow(penguins)`, and the number of female penguins being `r filter(penguins, sex == "female") |> nrow()`. We can also add footnotes[^1], and they will keep themselves numbered and placed correctly[^2]

[^1]: which can be very convenient

[^2]: without us really needing to keep it all in mind.

## Density

```{r}
#| label: fig-penguin-density
#| fig-cap: Penguin density by species
#| code-fold: true
penguins |> 
  pivot_longer(contains("_"),
               names_to = c("part",
                            "measure",
                            "unit"),
               names_sep = "_",
               values_to = "value") |> 
  ggplot(aes(x = value,
             fill = species)) + 
  geom_density() +
  facet_grid(part ~ measure, 
             scales = "free") +
  scale_fill_viridis_d(alpha = .7) +
  theme_minimal()
```

## summary

A summary of the observed penguin data can be found in @tbl-penguins. For this cross-reference to work, we *need* to have the `tbl-` prefix in the label name of the chunk that creates the table. The number of the table will update if another table appears before it, meaning you no longer need to deal with number your content correctly.\

# Table {.smaller}

```{r}
#| label: tbl-penguins
#| tbl-cap: Penguin summary
#| code-fold: true

penguins |> 
  pivot_longer(contains("_"),
               values_drop_na = TRUE) |> 
  group_by(name, species) |> 
  summarise(across(value, 
                   list(Mean = mean, 
                        SD = sd,
                        Min = min,
                        Max = max,
                        N = length),
                   .names = "{.fn}")) |> 
  mutate(
    name = str_replace_all(name, "_", " ")
  ) |> 
  kable(booktabs = TRUE, digits = 3) |> 
  kable_classic() |> 
  collapse_rows(1)
```

## Penguin models {.smaller}

```{r}
#| label: tbl-models
#| tbl-cap: Predicting bill length by bill depth, split by species and island.
#| code-fold: true
penguins |> 
  nest_by(species, island) |> 
  mutate(
    model = list(lm(bill_length_mm ~ bill_depth_mm,
                    data = data)),
    table = list(broom::tidy(model))
  ) |> 
  unnest(table) |> 
  select(-model, -data) |> 
  mutate(
    term = str_replace_all(term, "_", " ")
  ) |> 
  kable(booktabs = TRUE, digits = 3,) |> 
  kable_classic() |> 
  add_footnote("Models were run independently on data from the different island and species.",
               notation = "none") |> 
  collapse_rows(1:2)
```
